Supplementary information

### 2018-06-20 supplementary_information.Rmd
Remove deprecated plots. Add new correlation plot.

```{r correlation_sample_size_pairs, echo = FALSE, fig.cap = correlation_scatter_cap}
corr_results %>%
  mutate(
    significant = factor(significant, c("TRUE", "FALSE")) %>%
      forcats::lvls_revalue(c("yes", "no"))
  ) %>%
  ggplot() +
  aes(x = present + 0.1, y = Mean, color = significant) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  facet_wrap(~ pft) +
  scale_x_log10() +
  labs(x = "Sample size", y = "Correlation") +
  theme_bw() +
  theme(
	legend.position = "bottom"
  )
```

```{r correlation_sample_size_analysis, echo = FALSE, include = FALSE, eval = FALSE, fig.cap = correlation_fig_cap}
corr_binned <- corr_results %>%
  dplyr::mutate(
    ss_bin = cut(
      present,
      c(0, 1, 10, 25, 50, 100, 500, 1000, Inf),
      c("0", "< 10", "< 25", "< 50", "< 100", "< 500", "< 1000", "> 1000"),
      include.lowest = TRUE,
      right = FALSE
    )
  ) %>%
  group_by(pft, ss_bin) %>%
  summarize(frac_significant = mean(significant))

ggplot(corr_binned) +
  aes(x = ss_bin, y = frac_significant) +
  geom_segment(aes(xend = ss_bin, yend = 0)) +
  geom_point() +
  facet_wrap(~ pft) +
  labs(x = "Sample size", y = "Fraction of significant correlations") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 0.9))
```

>>>>

```{r correlation_sample_size_pairs, echo = FALSE, results = "hide", warning = FALSE, fig.cap = correlation_scatter_cap, fig.dim = c(12, 12)}
readd(corr_ss_plot_gg)
```
